Using SIMD and SIMT vectorization to evaluate sparse chemical kinetic Jacobian matrices and thermochemical source terms

### 2018-06-14 paper.tex
IR -> intermediate representation

In contrast,~\cref{F:pocl_source} shows the mean run time per condition of deep, shallow, and unvectorized OpenCL codes using the POCL runtime, as compared with OpenMP parallelization.
No speedup is achieved for either vectorization type on either CPU---indeed, the OpenMP case is faster on both CPUs\add{, though we stress that Intel OpenCL runtime achieves vectorization using the same code and hardware}.
The reasons for this lack of vectorization with POCL are quite technical~\delete{ and somewhat outside the scope of this work}; however, \add{personal communication with the developers of POCL revealed that to achieve vectorization, changes are required to both the way POCL prepares LLVM IR-code, as well as improvements to LLVM's loop-vectorizer itself~\cite{pocl_communication}.\footnote{Specifically, improvements such as ensuring LLVM recognizes uniform vectorization loop bounds (even if said bounds \textit{are} uniform in practice), proving vector instructions' ability to handle all edge cases identically to the corresponding scalar instruction, handing of branches and conditionals (potentially within POCL instructions themselves), and handling of memory access\slash vector-element extraction patterns.}}
As will be discussed in~\cref{S:opencl}, \add{we hope that using explicit vector types (to lessen demands on the LLVM-vectorization module) in combination with some of these changes might solve this issue}, but for the moment POCL is still quite useful as a validation tool.

>>>>

In contrast,~\cref{F:pocl_source} shows the mean run time per condition of deep, shallow, and unvectorized OpenCL codes using the POCL runtime, as compared with OpenMP parallelization.
No speedup is achieved for either vectorization type on either CPU---indeed, the OpenMP case is faster on both CPUs\add{, though we stress that Intel OpenCL runtime achieves vectorization using the same code and hardware}.
The reasons for this lack of vectorization with POCL are quite technical~\delete{ and somewhat outside the scope of this work}; however, \add{personal communication with the developers of POCL revealed that to achieve vectorization, changes are required to both the way POCL prepares LLVM intermediate representation code, as well as improvements to LLVM's loop-vectorizer itself~\cite{pocl_communication}.\footnote{Specifically, improvements such as ensuring LLVM recognizes uniform vectorization loop bounds (even if said bounds \textit{are} uniform in practice), proving vector instructions' ability to handle all edge cases identically to the corresponding scalar instruction, handing of branches and conditionals (potentially within POCL instructions themselves), and handling of memory access\slash vector-element extraction patterns.}}
As will be discussed in~\cref{S:opencl}, \add{we hope that using explicit vector types (to lessen demands on the LLVM-vectorization module) in combination with some of these changes might solve this issue}, but for the moment POCL is still quite useful as a validation tool.
